\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-03-21 paper/main.tex
Updated text

The following screencast demonstrates some
of the features of \tname:

\url{https://tinyurl.com/BugsInDLLs}\\
\Fix{Upload to YouTube with voiceover and add link here, archive 
the tool at zenodo}

@@

A developer needs to provide three scripts to integrate a fuzzing
tool: (1) a script that contains commands to run the tool; (2) a
preprocessing script to extract error types and buggy APIs for a
specific library version, and (3) a postprocessing script to match the
execution log with the expected errors needs to be provided. The
directory \CodeIn{tool-integration} that contains templates for these
scripts and their instantiations for FreeFuzz~\cite{wei2022free}, a
popular API fuzzer for DL libraries.
%
%% Tool execution proceeds in four steps: (1) Creation of Docker
%% container associated with a tool, (2) Reproduction of example bug from
%% the library version provided as input (3) Execution of preprocessing
%% script to extract error types and buggy APIs for a specific library
%% vesion (4) Execution of the tool and (5) Execution of postprocessing
%% script to match the execution log with the expected errors.

@@

\noindent
The script \CodeIn{install\_freefuzz\_docker.sh} contains the
following instructions\Fix{add brief explanation for what it does}:

@@

The next four steps are executed with \tname's command
\CodeIn{run-tool}.

When the command is run, firstly an example bug that is reproducible with the library version provided as an input is run as a sanity check. Then, a preprocessing script to extract error types and buggy APIs for a specific library version runs.
Then the environment inside
the docker container of the tool is updated to match the library version passed as an input and the fuzzing tool runs inside the enviroment. After the execution is complete, the next step is running a postprocessing script that checks the execution log against the error types of the bug to determine if the bugs were reproduced or not.
For example, the following command runs FreeFuzz
on version 2.2.0 from \torch.

@@

The script \CodeIn{run\_freefuzz\_docker.sh} contains instructions to run the preprocessing script, the tool, and the postprocessing script.
The output looks like the following:

@@

% \Fix{Abid, this does not make sense to me. If you are checking this
%   manually, you could run FreeFuzz separately and check manually. What
%   is the point?! You need to provide a list of bugs and check
%   automatically how many the tool can find (based on some criteria,
%   e.g, match the error message in Assertion or some n frames in the
%   stack (for crash)). --Marcelo}
After the execution completes, the output can be
checked for all failures produced by FreeFuzz (saved inside the
container) and manually inspected to see if any failure that can
reveal the bug in question was generated by the tool. In this case,
the failure generated by FreeFuzz could not generate a failure that
can reveal this bug since the API "torch.\_dynamo.export" is not
supported by FreeFuzz.

The execution log shows that the tool did not reproduce any of the
three bugs that were expected to be reproduced since the three buggy APIs \CodeIn{torch.fake\_quantize\_per\_channel\_affine}, \CodeIn{torch.all}, and \CodeIn{torch.compile} are not supported by FreeFuzz. The outputs of the tool are saved in the container and can be inspected manually to further inspect the execution log.

>>>>

The following video demonstrates some
of the features of \tname:

\url{https://www.youtube.com/watch?v=NslNWrULT1c}\\
% \Fix{Upload to YouTube with voiceover and add link here, archive 
% the tool at zenodo}

@@

A developer needs to provide three scripts to integrate a fuzzing
tool: (1) a script that contains commands to run the tool (e.g. \CodeIn{run\_freefuzz\_docker.sh}); (2) a
preprocessing script to extract error types and buggy APIs for a
specific library version (\CodeIn{preprocess.py}), and (3) a postprocessing script to match the
execution log with the expected errors (\CodeIn{postprocess.py}) needs to be provided.
% \Fix{name
%   these scripts here and refer back to them in the text below} 
The
directory \CodeIn{tool-integration} that contains templates for these
scripts and their instantiations for FreeFuzz~\cite{wei2022free}, a
popular API fuzzer for DL libraries.
% \Fix{remove this paragraph. Explain the steps when they appear. It is difficult
%   to follow}
% \Fix{up to here}

@@

\noindent
The script \CodeIn{install\_freefuzz\_docker.sh} build the docker container
that contains the tool FreeFuzz. The script contains the
following instructions:
% \Fix{add brief explanation for what it does}:

@@

\Fix{Please revise}
The command \CodeIn{run-tool} takes the library version as an input, along with the name of the docker container, the name of the library, and the script that contains the commands to run the tool (\CodeIn{run\_freefuzz\_docker.sh}) and it outputs how many bugs that are reproducible with this library version were successfully reproduced by a tool (e.g. FreeFuzz).
Tool execution proceeds as following. First, creation of docker
container associated with the tool done with the script \CodeIn{install\_freefuzz\_docker.sh}. 
Then an example bug that is reproducible with the library version provided as an input is run as a sanity check. 
Then the preprocessing
script (\CodeIn{preprocess.py}) is executed to extract error types and buggy APIs for a specific library
vesion. Then the environment inside
the docker container of the tool is updated to match the library version passed as an input and the fuzzing tool runs inside the enviroment. After the execution is complete, the next step is running a postprocessing script (\CodeIn{postprocess.py}) that checks the execution log against the error types of the bug to determine if the bugs were reproduced or not.

For example, the following command runs FreeFuzz
on version 2.2.0 from \torch.

@@

% The script \CodeIn{run\_freefuzz\_docker.sh} contains instructions to run the preprocessing script, the tool, and the postprocessing script.
The output looks like the following:

@@

% \Fix{Abid, this does not make sense to me. If you are checking this
%   manually, you could run FreeFuzz separately and check manually. What
%   is the point?! You need to provide a list of bugs and check
%   automatically how many the tool can find (based on some criteria,
%   e.g, match the error message in Assertion or some n frames in the
%   stack (for crash)). --Marcelo}
% After the execution completes, the output can be
% checked for all failures produced by FreeFuzz (saved inside the
% container) and manually inspected to see if any failure that can
% reveal the bug in question was generated by the tool. In this case,
% the failure generated by FreeFuzz could not generate a failure that
% can reveal this bug since the API "torch.\_dynamo.export" is not
% supported by FreeFuzz.
% \Fix{This is bad in two way: (1) we did not give
%   a chance to Freefuzz; unsupported API (2) it does not show any case
%   where the tool can reproduce the bug (and demo that our matchers
%   work). I hope you can do this on video or show another example to
%   complement this or modify this.}

\Fix{Abid: Added text to motivate adding support for these APIs, please revise}

The execution log shows that the tool did not reproduce any of the
three bugs that were expected to be reproduced since the three buggy APIs \CodeIn{torch.fake\_quantize\_per\_channel\_affine}, \CodeIn{torch.all}, and \CodeIn{torch.compile} are not supported by FreeFuzz. The outputs of the tool are saved in the container and can be inspected manually to further inspect the execution log. From this result, the developer can decide to add support for these three APIs in FreeFuzz and run the tool again to check if the bugs can be reproduced now. This will allow developers to decide on which APIs to add support for.
